Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England: Supplementary materials

### 2021-09-10 analysis/report/draft-supplement.Rmd
assume second dose occurs at the start of the day

#### Supplmentary Figure 1a: Comparative effectiveness using a minimally adjusted model

@@

#### Supplmentary Figure 1b: Comparative effectiveness using a demographically adjusted model

@@

#### Supplmentary Figure 2a: Second dose interval, where second dose vaccine is same as first dose vaccine

Second doses are censored by study end date, de-registration, death, and additionally by outcome-specific events.

@@

#### Supplmentary Figure 2b: Second dose interval, where second dose vaccine is different than the first dose vaccine

Second doses are censored by study end date, de-registration, death, and additionally by outcome-specific events.

```{r seconddose_diff, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'}
read_rds(here("output", "descriptive", "seconddose", "plot_seconddose_diffbrand.rds"))
```

#### Supplmentary Table 1: Baseline characteristics before eligibility exclusions

>>>>

#### Figure S1a: Comparative effectiveness adjusting for region-specific calendar-time

@@

#### Figure S1b: Comparative effectiveness adjusting for region-specific calendar-time and demographic characteristics

@@

#### Figure S2: Second dose interval

Second dose events are censored by study end date, de-registration, death, and additionally by outcome-specific events.

@@

<!-- #### Figure S2b: Second dose interval, where second dose vaccine is different than the first dose vaccine -->

<!-- Second doses are censored by study end date, de-registration, death, and additionally by outcome-specific events. -->

<!-- ```{r seconddose_diff, echo=FALSE, message=FALSE, warning=FALSE, out.width='90%', fig.height=8, results='asis'} -->

<!-- read_rds(here("output", "descriptive", "seconddose", "plot_seconddose_diffbrand.rds")) -->

<!-- ``` -->

#### Table S1: Baseline characteristics before eligibility exclusions
